Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
edit to two scale relationship

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. For B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.

>>>>

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. For B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of \citep{Chui1992}
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m}  p_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} q_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
 p_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
q_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
% and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients .
